Missing the Point: Convergence of Multiple Imputation using Chained Equations Algorithms

### 2020-03-20 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Run simulation to evaluate predictions (explained variance and stuff)
Removed stuff from Introduction

---
title: "Missing the Point: Convergence of Multiple Imputation using Chained Equations Algorithms"
author: "Hanne I. Oberman"
date: "16-3-2020"
output: 
  pdf_document:
    keep_tex: true
bibliography: thesis.bib
documentclass: sagej
classoption: Royal, times, sageapa
---

@@

# Background

- Focus on convergence, not evaluation of MI in general.

- Combine Theoretical Background and Intro.

At some point, any scientist conducting statistical analyses will run into a missing data problem [@alli02]. Missingness is problematic because statistical inference cannot be performed on incomplete data without employing \emph{ad hoc} solutions (e.g., list-wise deletion), which may yield wildly invalid results [@buur18]. A popular answer to the ubiquitous problem of missing information is to use the framework of multiple imputation (MI), proposed by @rubin87. MI is an iterative algorithmic procedure in which missing datapoints are `imputed' (i.e. filled in) several times. The variability between imputations is used to reflect how much uncertainty in the inference is introduced by the missingness. Therefore, MI can provide valid inferences despite missing information (**maybe add that this refers to CIs/p-values**).

To obtain valid inferences with MI, the variability between imputations should be properly represented [@rubin87; @buur18]. If this variability is under-estimated, confidence intervals around estimates will be too narrow, which can yield spurious results. Over-estimation of the variance between imputations results in unnecessarily wide confidence intervals, which can be costly because it lowers the statistical power (**maybe add why this is costly**). Since both of these situations are undesirable, imputations and their variability should be evaluated. Evaluation measures, however, are currently missing or under-developed in MI software, like the world-leading `mice` package [@mice] in `R` [@R]. 
The goal of this research project is to develop novel methodology and guidelines for evaluating MI methods. These tools will subsequently be implemented in an interactive evaluation framework for multiple imputation, which will aid applied researchers in drawing valid inference from incomplete datasets.

This note provides the theoretical foundation towards the diagnostic evaluation of multiple imputation algorithms. For reasons of brevity, we only focus on the MI algorithm implemented in `mice` [@mice]. The convergence properties of this MI algorithm are investigated through model-based simulation [^1]. The results of this simulation study are guidelines for assessing convergence of MI algorithms. 
<!-- These guidelines will be implemented in an interactive evaluation tool for `mice`, 'ShinyMICE', which is currently under development. We will evaluate how convergence of the MI algorithm can be diagnosed. -->

[^1]: All programming code used in this note is available from [github.com/gerkovink/shinyMice](https://github.com/gerkovink/shinyMice/tree/master/3.Thesis/1.SimulationStudy).

### Terminology

<!-- The intended audience of this note consists of anyone who uses multiple imputation to solve missing data problem.  -->
This note follows notation and conventions of `mice` [@mice]. 
<!-- Deviations from the 'original' notation by @rubin87 are described in [@buur18, \S~2.2.3].  -->
Basic familiarity with MI methodology is assumed. For the theoretical foundation of MI, see @rubin87. For an accessible and comprehensive introduction to MI from an applied perspective, see e.g. @buur18.

Let $Y$ denote an $n \times p$ matrix containing the data values on $p$ variables for all $n$ units in a sample. The collection of observed data values in $Y$ is denoted by $Y_{obs}$, and will be referred to as 'incomplete' or 'observed' data. The missing part of $Y$ is denoted by $Y_{mis}$. Which parts of $Y$ are missing is determined by the `missingness mechanism'.  
This note only considers a 'missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $Y$ [@rubin87].

@@

### Theoretical Background

There is no scientific consensus on the convergence properties of multiple imputation algorithms [@taka17]. Some default techniques in `mice` might not yield converged states at all [@murr18]. Therefore, algorithmic convergence should be monitored carefully. The diagnostic evaluation of convergence is preferred over the current practice---visually inspecting imputation chains for signs of non-convergence---since the latter may be challenging to the untrained eye [@buur18, \S~6.5.2].

The application of convergence diagnostics to MI methods has not been systematically studied [@buur18]. The measures that are available for diagnosing convergence of iterative algorithmic procedures (Markov chain Monte Carlo methods; e.g., `mice` algorithms or Gibbs samplers) generally evaluate signs of non-convergence [@hoff09]. Non-convergence may be present as non-stationarity within chains (i.e., trending), or as slow mixing between chains (i.e., no intermingling).

@@

\begin{align*}
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \text { where } s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}. 
<!-- %\text{ \cite[p.~5]{veht19}}  -->
\end{align*}

@@

\begin{align*}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \text { where } \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)}. 
<!-- %\text{ \cite[p.~5]{veht19}}  -->
\end{align*}

@@

### Simulation Hypothesis

@@

# Methods

@@

Data is simulated with the function `mvtnorm::rmvnorm()`, and outcome variable $Y$ is subsequently calculated as 
$$Y =  2X_1 + .5X_2 - X_3 + \epsilon .$$
The complete data is 'amputed' once for each simulation repetition. That is, the function `mice::ampute()` is used to impose a missingness mechanism upon the data. The missingness is univariate, and the probability to be missing is the same for all four variables, namely 20\% (`prop = 0.8, mech = "MCAR"`). This leaves 20\% of the rows completely observed. %The resulting amputed data is equal for all simulation conditions in the same repetition.

@@

- Remove the table.

@@

Figures 2 and 3 display results per simulation condition ($T = 1,2,\dots,100$).

>>>>

---
title: "Missing the Point: Convergence of Multiple Imputation by Chained Equations Algorithms"
author: "Hanne I. Oberman"
date: "16-3-2020"
output: 
  pdf_document:
    keep_tex: true
    number_sections: true
bibliography: thesis.bib
documentclass: sagej
classoption: Royal, times, sageapa
---

@@

# Introduction

At some point, any scientist conducting statistical analyses will run into a missing data problem [@alli02]. Missingness is problematic because statistical inference cannot be performed on incomplete data without employing \emph{ad hoc} solutions (e.g., list-wise deletion), which may yield wildly invalid results [@buur18]. A popular answer to the ubiquitous problem of missing information is to use the framework of multiple imputation (MI), proposed by @rubin87. For the theoretical foundation of MI, see @rubin87. For an accessible and comprehensive introduction to MI from an applied perspective, see e.g. @buur18. With MI, missing datapoints are 'imputed' (i.e., filled in) via an *imputation model*. The imputation model can be a joint model for all variables, or several univariate conditional distributions (fully conditional specification). FCS is more flexible and "avoids the problem of specifying an appropriate joint imputation distribution and replaces this by the selection of appropriate univariate conditional distributions". With FCS, an iterative algorithmic procedure is used to ... multiple imputation by chained equations ... "The values for imputing the missing data are drawn from the posterior predictive distribution of the missing data conditional on the observed data."  There is no scientific consensus on the convergence properties of FCS algorithms [@taka17]. Some default techniques in `mice` might not yield converged states at all [@murr18]. Therefore, algorithmic convergence should be monitored carefully.

Convergence cannot be determined for sure, because MICE is an MCMC method, and convergence of MCMC is not from scalar to a point, but from one distribution to another. Generated values will vary even after convergence. Therefore we can only diagnose non-convergence, not convergence [@hoff09]. "a weak diagnostics is better than no diagnostic at all" [@cowl96].

Current practice is visually inspecting imputation chains for signs of non-convergence, but may be challenging to the untrained eye [@buur18, \S~6.5.2]. Therefore diagnostic evaluation of convergence would be preferred. However, not known whether MCMC diagnostics are appropriate for MICE ... The application of convergence diagnostics to MI methods has not been systematically studied [@buur18]. How can non-convergence be diagnosed? How many iterations are sufficient/required? What are the effects of non-convergence on estimates, predictions and inference? What is an appropriate non-convergence diagnostic? Are the default number of iterations sufficient? Defaults in: SPSS (10; https://www.ibm.com/support/knowledgecenter/SSLVMB_24.0.0/spss/mva/syn_multiple_imputation_impute.html), Mplus (100??; https://pdfs.semanticscholar.org/e20e/29e008592cbfbaa567931f74cdfdb5451405.pdf?_ga=2.55354671.54033656.1584698748-527613517.1584698748), Stata (10; https://www.stata.com/manuals13/mi.pdf, p. 139), Amelia (NA, because resampling, not convergence; https://cran.r-project.org/web/packages/Amelia/Amelia.pdf), en MI (30; https://cran.r-project.org/web/packages/mi/mi.pdf).

For reasons of brevity, we only focus on the MI algorithm implemented in the world-leading MI software: the `R` [@R] package `mice` [@mice]. The convergence properties of this MI algorithm are investigated through model-based simulation. The results of this simulation study are guidelines for assessing convergence of MI algorithms, which will aid applied researchers in drawing valid inference from incomplete datasets.

<!-- MI is an iterative algorithmic procedure in which missing datapoints are `imputed' (i.e. filled in) several times. The variability between imputations is used to reflect how much uncertainty in the inference is introduced by the missingness. Therefore, MI can provide valid inferences despite missing information (**maybe add that this refers to CIs/p-values**).  -->

<!-- To obtain valid inferences with MI, the variability between imputations should be properly represented [@rubin87; @buur18]. If this variability is under-estimated, confidence intervals around estimates will be too narrow, which can yield spurious results. Over-estimation of the variance between imputations results in unnecessarily wide confidence intervals, which can be costly because it lowers the statistical power (**maybe add why this is costly**). Since both of these situations are undesirable, imputations and their variability should be evaluated. Evaluation measures, however, are currently missing or under-developed in MI software, like the world-leading `mice` package [@mice] in `R` [@R].  -->
<!-- The goal of this research project is to develop novel methodology and guidelines for evaluating MI methods. These tools will subsequently be implemented in an interactive evaluation framework for multiple imputation, which will aid applied researchers in drawing valid inference from incomplete datasets.  -->

<!-- This note provides the theoretical foundation towards the diagnostic evaluation of multiple imputation algorithms. For reasons of brevity, we only focus on the MI algorithm implemented in `mice` [@mice]. The convergence properties of this MI algorithm are investigated through model-based simulation. The results of this simulation study are guidelines for assessing convergence of MI algorithms.  -->
<!-- These guidelines will be implemented in an interactive evaluation tool for `mice`, 'ShinyMICE', which is currently under development. We will evaluate how convergence of the MI algorithm can be diagnosed. -->

<!-- [^1]: All programming code used in this note is available from [github.com/gerkovink/shinyMice](https://github.com/gerkovink/shinyMice/tree/master/3.Thesis/1.SimulationStudy). -->

## Terminology

<!-- The intended audience of this note consists of anyone who uses multiple imputation to solve missing data problem.  -->
This note follows notation and conventions of `mice` [@mice].
<!-- Deviations from the 'original' notation by @rubin87 are described in [@buur18, \S~2.2.3].  -->
<!-- Basic familiarity with MI methodology is assumed.   -->

Let $Y$ denote an $n \times p$ matrix containing the data values on $p$ variables for all $n$ units in a sample. The collection of observed data values in $Y$ is denoted by $Y_{obs}$, and will be referred to as 'incomplete' or 'observed' data. The missing part of $Y$ is denoted by $Y_{mis}$. Which parts of $Y$ are missing is determined by the 'missingness mechanism'.

@@

# Convergence diagnostics

In iterative algorithmic procedures (Markov chain Monte Carlo methods; e.g., `mice` algorithms or Gibbs samplers) non-convergence may be present as non-stationarity within chains (i.e., trending), or as slow mixing between chains (i.e., no intermingling).

@@

\begin{align*}
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \text { where } s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}. 
\end{align*}
<!-- %\text{ \cite[p.~5]{veht19}}  -->

@@

\begin{align*}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \text { where } \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)}. 
\end{align*}
<!-- %\text{ \cite[p.~5]{veht19}}  -->

@@

## Simulation Hypothesis

@@

# Simulation study

@@

Data is simulated with the function `mvtnorm::rmvnorm()`, and outcome variable $Y$ is subsequently calculated as 
$$Y =  2X_1 + .5X_2 - X_3 + \epsilon .$$
This note only considers a 'missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $Y$ [@rubin87]. The complete data is 'amputed' once for each simulation repetition. That is, the function `mice::ampute()` is used to impose a missingness mechanism upon the data. The missingness is univariate, and the probability to be missing is the same for all four variables, namely 20\% (`prop = 0.8, mech = "MCAR"`). This leaves 20\% of the rows completely observed. %The resulting amputed data is equal for all simulation conditions in the same repetition.

@@

@@

<!-- Figures 2 and 3 display results per simulation condition ($T = 1,2,\dots,100$).  -->

### 2020-03-20 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Run simulation to evaluate predictions (explained variance and stuff)
Removed stuff from Introduction

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

\hypertarget{background}{%
\section{Background}\label{background}}

\begin{itemize}
\item
  Focus on convergence, not evaluation of MI in general.
\item
  Combine Theoretical Background and Intro.
\end{itemize}

At some point, any scientist conducting statistical analyses will run
into a missing data problem (Allison 2001). Missingness is problematic
because statistical inference cannot be performed on incomplete data
without employing \emph{ad hoc} solutions (e.g., list-wise deletion),
which may yield wildly invalid results (Van Buuren 2018). A popular
answer to the ubiquitous problem of missing information is to use the
framework of multiple imputation (MI), proposed by Rubin (1987). MI is
an iterative algorithmic procedure in which missing datapoints are
`imputed' (i.e.~filled in) several times. The variability between
imputations is used to reflect how much uncertainty in the inference is
introduced by the missingness. Therefore, MI can provide valid
inferences despite missing information (\textbf{maybe add that this
refers to CIs/p-values}).

To obtain valid inferences with MI, the variability between imputations
should be properly represented (Rubin 1987; Van Buuren 2018). If this
variability is under-estimated, confidence intervals around estimates
will be too narrow, which can yield spurious results. Over-estimation of
the variance between imputations results in unnecessarily wide
confidence intervals, which can be costly because it lowers the
statistical power (\textbf{maybe add why this is costly}). Since both of
these situations are undesirable, imputations and their variability
should be evaluated. Evaluation measures, however, are currently missing
or under-developed in MI software, like the world-leading \texttt{mice}
package (Van Buuren and Groothuis-Oudshoorn 2011) in \texttt{R} (R Core
Team 2019). The goal of this research project is to develop novel
methodology and guidelines for evaluating MI methods. These tools will
subsequently be implemented in an interactive evaluation framework for
multiple imputation, which will aid applied researchers in drawing valid
inference from incomplete datasets.

This note provides the theoretical foundation towards the diagnostic
evaluation of multiple imputation algorithms. For reasons of brevity, we
only focus on the MI algorithm implemented in \texttt{mice} (Van Buuren
and Groothuis-Oudshoorn 2011). The convergence properties of this MI
algorithm are investigated through model-based simulation.\footnote{All
  programming code used in this note is available from
  \href{https://github.com/gerkovink/shinyMice/tree/master/3.Thesis/1.SimulationStudy}{github.com/gerkovink/shinyMice}.}
The results of this simulation study are guidelines for assessing
convergence of MI algorithms.

\hypertarget{terminology}{%
\subsubsection{Terminology}\label{terminology}}

This note follows notation and conventions of \texttt{mice} (Van Buuren
and Groothuis-Oudshoorn 2011). Basic familiarity with MI methodology is
assumed. For the theoretical foundation of MI, see Rubin (1987). For an
accessible and comprehensive introduction to MI from an applied
perspective, see e.g.~Van Buuren (2018).

@@

\hypertarget{theoretical-background}{%
\subsubsection{Theoretical Background}\label{theoretical-background}}

There is no scientific consensus on the convergence properties of
multiple imputation algorithms (Takahashi 2017). Some default techniques
in \texttt{mice} might not yield converged states at all (Murray 2018).
Therefore, algorithmic convergence should be monitored carefully. The
diagnostic evaluation of convergence is preferred over the current
practice---visually inspecting imputation chains for signs of
non-convergence---since the latter may be challenging to the untrained
eye (Van Buuren 2018, \textasciitilde6.5.2).

The application of convergence diagnostics to MI methods has not been
systematically studied (Van Buuren 2018). The measures that are
available for diagnosing convergence of iterative algorithmic procedures
(Markov chain Monte Carlo methods; e.g., \texttt{mice} algorithms or
Gibbs samplers) generally evaluate signs of non-convergence (Hoff 2009).
Non-convergence may be present as non-stationarity within chains (i.e.,
trending), or as slow mixing between chains (i.e., no intermingling).

@@

\begin{align*}
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \text { where } s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}. 
<!-- %\text{ \cite[p.~5]{veht19}}  -->
\end{align*}

@@

\begin{align*}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \text { where } \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)}. 
<!-- %\text{ \cite[p.~5]{veht19}}  -->
\end{align*}

@@

\hypertarget{simulation-hypothesis}{%
\subsubsection{Simulation Hypothesis}\label{simulation-hypothesis}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{convergence-diagnostics}{%
\subsubsection{Convergence Diagnostics}\label{convergence-diagnostics}}

>>>>

\setcounter{secnumdepth}{5}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

At some point, any scientist conducting statistical analyses will run
into a missing data problem (Allison 2001). Missingness is problematic
because statistical inference cannot be performed on incomplete data
without employing \emph{ad hoc} solutions (e.g., list-wise deletion),
which may yield wildly invalid results (Van Buuren 2018). A popular
answer to the ubiquitous problem of missing information is to use the
framework of multiple imputation (MI), proposed by Rubin (1987). For the
theoretical foundation of MI, see Rubin (1987). For an accessible and
comprehensive introduction to MI from an applied perspective, see
e.g.~Van Buuren (2018). With MI, missing datapoints are `imputed' (i.e.,
filled in) via an \emph{imputation model}. The imputation model can be a
joint model for all variables, or several univariate conditional
distributions (fully conditional specification). FCS is more flexible
and ``avoids the problem of specifying an appropriate joint imputation
distribution and replaces this by the selection of appropriate
univariate conditional distributions''. With FCS, an iterative
algorithmic procedure is used to \ldots{} multiple imputation using
chained equations \ldots{} ``The values for imputing the missing data
are drawn from the posterior predictive distribution of the missing data
conditional on the observed data.'' There is no scientific consensus on
the convergence properties of FCS algorithms (Takahashi 2017). Some
default techniques in \texttt{mice} might not yield converged states at
all (Murray 2018). Therefore, algorithmic convergence should be
monitored carefully.

Current practice is visually inspecting imputation chains for signs of
non-convergence, but may be challenging to the untrained eye (Van Buuren
2018, \textasciitilde6.5.2). Therefore diagnostic evaluation of
convergence would be preferred. However, not known whether MCMC
diagnostics are appropriate for MICE \ldots{} The application of
convergence diagnostics to MI methods has not been systematically
studied (Van Buuren 2018). How can non-convergence be diagnosed? How
many iterations are sufficient/required? What are the effects of
non-convergence on estimates, predictions and inference? What is an
appropriate non-convergence diagnostic? Are the default number of
iterations sufficient?

Convergence cannot be determined for sure, because MICE is an MCMC
method, and convergence of MCMC is not from scalar to a point, but from
one distribution to another. Generated values will vary even after
convergence. Therefore we can only diagnose non-convergence, not
convergence (Hoff 2009). ``a weak diagnostics is better than no
diagnostic at all'' (Cowles and Carlin 1996).

Defaults is: SPSS (10;
\url{https://www.ibm.com/support/knowledgecenter/SSLVMB_24.0.0/spss/mva/syn_multiple_imputation_impute.html}),
Mplus (100??;
\url{https://pdfs.semanticscholar.org/e20e/29e008592cbfbaa567931f74cdfdb5451405.pdf?_ga=2.55354671.54033656.1584698748-527613517.1584698748}),
Stata (10; \url{https://www.stata.com/manuals13/mi.pdf}, p.~139), Amelia
(NA, because resampling, not convergence;
\url{https://cran.r-project.org/web/packages/Amelia/Amelia.pdf}), en MI
(30; \url{https://cran.r-project.org/web/packages/mi/mi.pdf}).

For reasons of brevity, we only focus on the MI algorithm implemented in
the world-leading MI software: the \texttt{R} (R Core Team 2019) package
\texttt{mice} (Van Buuren and Groothuis-Oudshoorn 2011). The convergence
properties of this MI algorithm are investigated through model-based
simulation. The results of this simulation study are guidelines for
assessing convergence of MI algorithms, which will aid applied
researchers in drawing valid inference from incomplete datasets.

\hypertarget{terminology}{%
\subsection{Terminology}\label{terminology}}

@@

\hypertarget{convergence-diagnostics}{%
\section{Convergence diagnostics}\label{convergence-diagnostics}}

In iterative algorithmic procedures (Markov chain Monte Carlo methods;
e.g., \texttt{mice} algorithms or Gibbs samplers) non-convergence may be
present as non-stationarity within chains (i.e., trending), or as slow
mixing between chains (i.e., no intermingling).

@@

\begin{align*}
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \text { where } s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}. 
\end{align*}

@@

\begin{align*}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \text { where } \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)}. 
\end{align*}

@@

\hypertarget{simulation-hypothesis}{%
\subsection{Simulation Hypothesis}\label{simulation-hypothesis}}

@@

\hypertarget{simulation-study}{%
\section{Simulation study}\label{simulation-study}}

@@

\hypertarget{convergence-diagnostics-1}{%
\subsubsection{Convergence
Diagnostics}\label{convergence-diagnostics-1}}
